Missing data: Current practice in football research and recommendations for

### 2020-10-04 paper/paper.Rmd
edit conclusion.

Our survey of 2019 articles on football related topics
showed that current practice of reporting missing data is poor, 
with only about one in 20 studies reporting missing data.
We speculate that this result is representative of practice in the 
wider sports science literature. The extremely low reporting of missing 
data could suggest that this aspect of data anlaysis receives little attention. 
To address this issue and assist researchers,
we have provided recommendations for reporting and exploring missing data.
Researchers should consider these recommendations, and pay greater
attention to missing data and its influence on research results.

>>>>

Our survey of articles on football related topics
showed that current practice of reporting missing data is poor, 
with only about one in 20 studies reporting missingness.
We speculate that this result is representative of practice in the 
wider sports science literature. The extremely low reporting of missing 
data could suggest that this aspect of anlaysis receives little attention. 
To address this issue and assist researchers,
we have provided recommendations for reporting and exploring missing data.
Researchers should consider these recommendations, and pay greater
attention to missing data and its influence on research results.
